A Unification of Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-20 colt-21/cvx-flats.tex
comments

\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
	Given target property $\gamma:\P \toto \R$, if there is some $p \in \P$ such that $|\gamma(p)| = 1$ with $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$
	Moreover, if there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{thm:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
	Moreover, by construction of such a flat, we know the \Pcodimension is at most $d$.
	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
	Thus, we have $p \in F \subseteq \gamma_r$.

@@

\begin{corollary}\label{cor:Pcodim-flat-elic-relint-prop} 
	Given target property $\gamma:\P \toto \reals^d$, where $\P$ is defined over a finite set of outcomes $\Y$.
	For all $p \in \relint{\P}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
	Moreover, if there is some $p \in \relint{\P}$ so that there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$, and suppose $r' = \psi(u)$.
	Take $F \subseteq \Gamma_u$ to be the flat that exists by Lemma~\ref{thm:convex-flats-inf-dim}.
	If $r = r'$, then $p \in F \subseteq \Gamma_u \subseteq \gamma_r$ by indirect elicitation.
	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.

>>>>

\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
  Let target property $\gamma:\P \toto \R$ be given.
  \raf{You are missing $d$ here, and the indirect elicitation via convex surrogate.}
  If there is some $p \in \P$ with $|\gamma(p)| = 1$, then letting $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
  In particular, if there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{thm:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
	Moreover, by construction of such a flat, we know the \Pcodimension is at most $d$.
	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
	Thus, we have $p \in F \subseteq \gamma_r$.

@@

\begin{corollary}\label{cor:Pcodim-flat-elic-relint-prop} 
  Given target property $\gamma:\P \toto \reals^d$, \raf{$\R$ right?} where $\P\subseteq\simplex$ for a finite set of outcomes $\Y$.
  \raf{Missing $d$ and ind elic again}
	For all $p \in \relint{\P}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
	Moreover, if there is some $p \in \relint{\P}$ so that there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$, and suppose $r' = \psi(u)$.
	Take $F \subseteq \Gamma_u$ to be the flat that exists by Lemma~\ref{thm:convex-flats-inf-dim}.
	If $r = r'$, then $p \in F \subseteq \Gamma_u \subseteq \gamma_r$ by indirect elicitation.
	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.
